The \dealii Library, Version 9.2

### 2020-04-24 9.2/paper.tex
Make myself co-author

\hypersetup{
  pdfauthor={
%     Daniel Arndt,
%     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
%     Martin Kronbichler,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

% %
% \author[8]{Luca~Heltai}
% \affil[8]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
%   {\texttt{luca.heltai@sissa.it}}}
% 
% \author[9]{Martin~Kronbichler}
% \affil[9]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
% 
% \author[11]{Matthias~Maier}
% \affil[11]{Department of Mathematics,
%   Texas A\&M University,
%   3368 TAMU,
%   College Station, TX 77845, USA.
%   {\texttt{maier@math.tamu.edu}}}
% 
% \author[4]{Jean-Paul~Pelteret}
% 
% \author[*1]{Bruno~Turcksin}
% 
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}

@@

In addition, there are four new tutorial programs and one new code
gallery program:
\begin{itemize}
\item 
% \texttt{step-61} is a program that implements the ``weak
%   Galerkin'' method to solve the Laplace equation. Weak Galerkin
%   methods are related to the Hybridized Discontinuous Galerkin method
%   in that they introduce degrees of freedom on the interfaces between
%   cells, but they do not require the reformulation of the problem as a
%   first-order system and instead re-define what the gradient of a
%   discontinuous function is.
% 
% \item \texttt{step-62} demonstrates the solution of problems related
%   to phononic or photonic crystals. Among the techniques shown in this
%   program is the solution of complex-valued linear systems, and the
%   use of absorbing boundary conditions through the Perfectly Matched
%   Layer technique.
% 
% \item \texttt{step-63} implements a geometric multigrid preconditioner
%   and solver for the advection-diffusion equation, yielding optimal
%   complexity. The tutorial compares
%   point-based smoothers to cell-based smoothers and
%   demonstrates the effect of downstream ordering on smoother performance.
% 
% \item \texttt{step-64} demonstrates the usage of matrix-free methods on Nvidia GPUs.
% GPUs are shown to be advantageous for these kind of operations because of their superior
% hardware characteristics, in particular a higher memory bandwidth than server
% CPUs within a given power envelope.
% 
% \item The \texttt{MCMC-Laplace} code gallery program is a code useful
%   for the forward solution used as a building block in
%   Bayesian inverse problems, and for sampling the parameter space
%   through a Metropolis--Hastings sampler (a kind of Monte Carlo
%   Markov Chain method).
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}
     {around 15 incompatible changes}; see \cite{changes91}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

The two previous releases of \dealii can be cited as
\cite{dealII85,dealII90}.

>>>>

\hypersetup{
  pdfauthor={
%     Daniel Arndt,
%     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

% %
% \author[8]{Luca~Heltai}
% \affil[8]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
%   {\texttt{luca.heltai@sissa.it}}}
%
 \author[9]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler@lnm.mw.tum.de}}}
%
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
%
% \author[11]{Matthias~Maier}
% \affil[11]{Department of Mathematics,
%   Texas A\&M University,
%   3368 TAMU,
%   College Station, TX 77845, USA.
%   {\texttt{maier@math.tamu.edu}}}
%
% \author[4]{Jean-Paul~Pelteret}
%
% \author[*1]{Bruno~Turcksin}
%
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\item \texttt{step-50}
\item \texttt{step-58}
\item \texttt{step-65}
\item \texttt{step-67}
\item \texttt{step-69}
\item \texttt{step-70}
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 15 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

The two previous releases of \dealii can be cited as
\cite{dealII90,dealII91}.
